---
title: "larval-size"
author: "Laura H Spencer"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(readxl)
require(here)
require(purrr)
require(plotly)

```

Read in size data, join with sample info 

```{r}
# Data collected using Jackie's scope, but done so in numerical order, which was not random. 
# larvalsize.path.old <- here::here("data", "new-larvae-size", "20191111_2018-new-larvae.xlsx")
# larvalsize.old <- larvalsize.path.old %>%
#   excel_sheets() %>%
#   set_names() %>%
#   purrr::map_df(~ read_excel(path = larvalsize.path.old, sheet = .x), .id = "sheet") %>%
#   dplyr::mutate(Sample.number = as.numeric(sheet)) %>% 
#   inner_join(
#     readRDS(file=here::here("data/larvae-collection-data.rds")) %>% 
#       as_tibble() %>%
#       dplyr::select(Rep, Date, Bag, Group, Sample.number, Live.Larvae, TEMP, FOOD, TREAT) %>%
#       dplyr::mutate(Sample.number = as.numeric(Sample.number)))

# Data re-collected using Jackie's scope, in random order. 
larvalsize.path <- here::here("data", "new-larvae-size", "20200110_2018-new-larvae.xlsx")
larvalsize <- larvalsize.path %>%
  excel_sheets() %>%
  set_names() %>%
  purrr::map_df(~ read_excel(path = larvalsize.path, sheet = .x), .id = "sheet") %>%
  dplyr::mutate(Sample.number = as.numeric(sheet)) %>% 
  inner_join(
    readRDS(file=here::here("data/larvae-collection-data.rds")) %>% 
      as_tibble() %>%
      dplyr::select(Rep, Date, Bag, Group, Sample.number, Live.Larvae, TEMP, FOOD, TREAT) %>%
      dplyr::mutate(Sample.number = as.numeric(Sample.number)))
```

How many larvae were measured per sample? 

```{r}
ngroups <- larvalsize %>% group_by(sheet) %>% tally()
```


Create a dataframe with average shell measurements by sample number (aka larval batch)

```{r}
average.all <- larvalsize %>% 
  dplyr::select(sheet, MaxFeret, MinFeret, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group, Live.Larvae) %>%
  mutate(sheet=as.numeric(larvalsize$sheet)) %>%
  group_by(sheet) %>%
  mutate_at(c("MaxFeret", "MinFeret", "Circularity", "Length", "Width", "Live.Larvae"), mean, na.rm=TRUE) %>%
  distinct() %>%
  mutate(ethanol=ifelse(sheet < 50, 'YES', 'NO')) %>%
  drop_na("sheet")
```

# Plots

## Length & Width by release date 

```{r}
ggplotly(average.all %>% 
ggplot(aes(x=sheet, y=Length, col=FOOD:TEMP)) + theme(legend.position="bottom", 
       axis.text.x = element_text(angle = 90, hjust = 1, size = 6)) + 
  ggtitle("Length, proxy for shell width") + geom_point())

ggplotly(average.all %>% 
ggplot(aes(x=sheet, y=Width, col=FOOD:TEMP)) + theme(legend.position="bottom", 
       axis.text.x = element_text(angle = 90, hjust = 1, size = 6)) + 
  ggtitle("Width, proxy for shell height") + geom_point())
```

## Shell size by circulatiry (which may influence how accurate measurements were)

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Circularity, y=Length, col=FOOD:TEMP)) + 
  geom_point() + ggtitle("Length, proxy for shell width") +
  geom_smooth(method = "lm", alpha = .15, aes(fill = FOOD:TEMP)))

ggplotly(average.all %>%
ggplot(aes(x=Circularity, y=Width, col=FOOD:TEMP)) + 
  geom_point() + ggtitle("Width, proxy for shell height") +
  geom_smooth(method = "lm", alpha = .15, aes(fill = FOOD:TEMP)))
```

## Shell size by date released 

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Date, y=Length, col=FOOD:TEMP)) + 
  geom_point() + 
  geom_smooth(method = "lm", alpha = .15, aes(fill = FOOD:TEMP)))

ggplotly(average.all %>%
ggplot(aes(x=Date, y=Width, col=FOOD:TEMP)) + 
  geom_point() + 
  geom_smooth(method = "lm", alpha = .15, aes(fill = FOOD:TEMP)))
```

## Circularity by release date

### NOTE: it is clear that samples #1-50 were preserved well, but samples >#50 were considerably degraded (ethanol was not used to kill the larvae)

```{r}
ggplotly(average.all %>%
ggplot(aes(x=sheet, y=Circularity, col=FOOD:TEMP)) + 
  geom_point())
```

## Shell length by # larvae collected that day 

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Live.Larvae, y=Length, col=FOOD:TEMP)) + 
  geom_point())
```


```{r}
### plot old vs. new measurements - different? 

old.new <- merge(
  x=larvalsize.old %>% 
  dplyr::select(sheet, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group) %>%
  group_by(sheet) %>%
  mutate_at(c("Length", "Width", "Circularity"), mean, na.rm=TRUE) %>%
  distinct(),
  y=larvalsize %>% 
  dplyr::select(sheet, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group) %>%
  group_by(sheet) %>%
  mutate_at(c("Length", "Width", "Circularity"), mean, na.rm=TRUE) %>%
  distinct(),
  by="sheet") 

summary(lm(Length.y ~ Length.x, data=old.new))

ggplotly(ggplot(data=old.new, aes(x=Length.x, y=Length.y, col=TEMP.x:FOOD.x)) + 
  geom_point() + geom_smooth(method = "lm"))

ggplotly(ggplot(data=old.new, aes(x=Length.x, y=Length.y)) + 
  geom_point() + geom_smooth(method = "lm"))

```

### Boxplots analysis of size metrics by treatment, all larvae measured 

### Length (aka shell width)

```{r}
# If I want to use subsample of larval size data for balanced design 
# test <- average.all %>% 
#   group_by(FOOD, TEMP) %>%
#   sample_n(12)

# Plot shell width (aka length in data) by treatment, and by ethanol preservation 
# Note: I killed larvae using ethanol through sample 50, then stopped. This significantly altered the integrity of the larval samples (ethanol = well preserved), which altered the general size measurement. I therefore will include "ethanol" as a random variable in my models when I test effect of parental treatments 

average.all %>% 
  group_by(FOOD, TEMP) %>% 
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  ggtitle("Length by treatment (and preservation method)") + 
  theme_minimal() +
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) +
  facet_wrap(~ethanol)

hist(average.all$Length)
shapiro.test(average.all$Length) #Data is normal 

bartlett.test(average.all$Length ~ average.all$FOOD)
bartlett.test(average.all$Length ~ average.all$TEMP) # variance not homogenous between temperatures
leveneTest(Length~FOOD*TEMP, data=average.all)  # Use Levene test to compare across all 4 treatments. Variance doesn't differ. 
# Balanced design? No. 
table(average.all$TEMP:average.all$FOOD) #how many larval groups per treatment?

# Include the "ethanol" random factor, since that presrevation method resulted in varying size
Anova(lme(Length ~  FOOD*TEMP, random=~1|ethanol,data=average.all))
anova(lm(Length ~  Circularity*FOOD*TEMP,data=average.all))
anova(lm(Length ~  Date*FOOD*TEMP,data=average.all))

# Do type II ANOVA, since unbalanced design. and unequal variances. No diff. 
Anova(lme(Length ~  FOOD*TEMP, random=~1|ethanol,data=average.all), type="II", white.adjust=TRUE) #same result

# Look at effect directly 
summary(lme(Length ~  FOOD*TEMP, random=~1|ethanol,data=average.all))

# Effect of ethanol preservation: -5.620869 
# Create new column that corrects data for differences in ethanol preservation 

average.all <- mutate(average.all, Length.corr=if (ethanol=="NO"){Length-5.620869}
    else if (ethanol=="YES"){Length})

# Relevel food factors such that Low comes before High
average.all$FOOD <- factor(average.all$FOOD, levels = rev(levels(average.all$FOOD)))

pdf(file=here::here("results","larval-shell-length-remeasure.pdf"), width = 4, height = 7)
average.all %>%
ggplot(aes(x=FOOD:TEMP, y=Length.corr)) + 
geom_boxplot(lwd=0.5, aes(col=FOOD:TEMP)) + 
  theme_bw(base_size = 13) + 
  labs(title="Larval shell width upon release", y=("shell width (µm), corrected"), x="treatment") + 
  scale_color_manual(values=c('#92c5de','#f4a582','#0571b0','#ca0020'), name=element_blank(), 
  labels = c("Low-food+7°C","Low-food+10°C","High-food+7°C","High-food+10°C")) + 
  theme(text = element_text(size = 12.5)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none") + 
  ylim(c(160, 205)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP))
dev.off()

pdf(file=here::here("results","larval-shell-length-ethanol.pdf"), width = 10, height = 6)
average.all %>%
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
#geom_boxplot(lwd=0.5, aes(col=FOOD:TEMP)) + 
  theme_bw(base_size = 13) + 
  labs(title="Larval shell width upon release\nby parental treatment, and use of ethanol during preservation", 
       y=("shell width (µm)"), x="treatment") + 
  scale_color_manual(values=c('#92c5de','#f4a582','#0571b0','#ca0020'), name=element_blank(), 
  labels = c("Low-food+7°C","Low-food+10°C","High-food+7°C","High-food+10°C")) + 
  theme(text = element_text(size = 12),
        axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ylim(c(160, 205)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) + 
    guides(colour = guide_legend(override.aes = list(size = 4.5))) #+
  facet_wrap(~ethanol)
dev.off()


# Conclusion: Larval shell Length (aka widh in data) affected by parental temperature, larger from adults held in elevated temperature. Effect was most pronounced when also fed high food. No effect of food alone.

aggregate(Length ~ FOOD, data=average.all, mean) #Larger larvae from higher food 
aggregate(Length ~ FOOD, data=average.all, sd)

aggregate(Length ~ FOOD:TEMP, data=average.all, mean)
aggregate(Length ~ FOOD:TEMP, data=average.all, sd)

aggregate(Width ~ FOOD:TEMP, data=average.all, mean)
aggregate(Width ~ FOOD:TEMP, data=average.all, sd)

```

### Width (aka shell height)

```{r}
average.all %>% 
  group_by(FOOD, TEMP) %>% 
ggplot(aes(x=FOOD:TEMP, y=Width)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  ggtitle("Width by treatment (and preservation method)") + 
  theme_minimal() +
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) +
  facet_wrap(~ethanol)

hist(average.all$Width)
shapiro.test(average.all$Width^2) #Data is normal 

bartlett.test(average.all$Width^2 ~ average.all$FOOD)
bartlett.test(average.all$Width^2 ~ average.all$TEMP) # variance not homogenous between temperatures
leveneTest(Width^2~FOOD*TEMP, data=average.all)  # Use Levene test to compare across all 4 treatments. Variance doesn't differ. 
# Balanced design? No. 
table(average.all$TEMP:average.all$FOOD) #how many larval groups per treatment?

# Include the "ethanol" random factor, since that preservation method resulted in varying size
Anova(lme(Width^2 ~  FOOD*TEMP, random=~1|ethanol,data=average.all,method="REML"))
?Anova()
# Do type II ANOVA, since unbalanced design. and unequal variances. No diff. 
Anova(lme(Width^2 ~  FOOD*TEMP, random=~1|ethanol,data=average.all,method="REML"), type="II", white.adjust=TRUE) #same result 

# Conclusion: Larval shell height (aka width in data) unaffected by parental winter food or temperature treatment.  
```

# Assess larval size differences among only larval groups that I reared, by broodstock treatment

```{r}
average.reared <- larvalsize %>% 
  dplyr::select(sheet, MaxFeret, MinFeret, Circularity, Length, Width, Sample.number, Date, TEMP, FOOD, Group) %>%
  filter(!is.na(Group)) %>%
  group_by(sheet) %>%
  mutate_at(c("MaxFeret", "MinFeret", "Circularity", "Length", "Width"), mean, na.rm=TRUE) %>%
  distinct()
```

## Length (aka shell width)

```{r}
average.reared %>%
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) 

hist(average.reared$Length)
shapiro.test(average.reared$Length)
bartlett.test(average.reared$Length ~ average.reared$TEMP)
bartlett.test(average.reared$Length ~ average.reared$FOOD)
summary(aov(Length ~ FOOD*TEMP, data=average.reared)) #Food sign. 
TukeyHSD(aov(Length ~ FOOD*TEMP, data=average.reared)) #Larger larvae from high food 
summary(aov(Length ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(Length ~ FOOD:TEMP, data=average.reared))
```

## Width (aka shell height)

```{r}
average.reared %>%
ggplot(aes(x=FOOD:TEMP, y=Width)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) 

hist(average.reared$Width)
shapiro.test(average.reared$Width)
bartlett.test(average.reared$Width ~ average.reared$TEMP)
bartlett.test(average.reared$Width ~ average.reared$FOOD)
summary(aov(Width ~ FOOD*TEMP, data=average.reared)) #Food sign. 
TukeyHSD(aov(Width ~ FOOD*TEMP, data=average.reared)) #Lager larvae from high food 
summary(aov(Width ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(Width ~ FOOD:TEMP, data=average.reared))

summary(aov(Width ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))

average.reared %>%
ggplot(aes(x=Circularity, y=Width)) + 
  geom_point(aes(col=TEMP)) 
```

## Figures 

### Shell width (longest axis, but referred to as "length" in data), all measured larvae 

```{r}
# Relevel food factors such that Low comes before High
average.all$FOOD <- factor(average.all$FOOD, levels = rev(levels(average.all$FOOD)))

pdf(file=here::here("results","larval-shell-length-remeasure.pdf"), width = 6, height = 6)
average.all %>%
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=FOOD:TEMP)) + 
  theme_bw(base_size = 13) + 
  labs(title="Larval shell width upon release", y=("shell width (µm)"), x="treatment") + 
  scale_color_manual(values=c('#92c5de','#f4a582','#0571b0','#ca0020'), name=element_blank(), 
  labels = c("Low-food+7°C","Low-food+10°C","High-food+7°C"," High-food+10°C")) + 
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  ylim(c(160, 215)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP))
dev.off()

summary(aov(Length ~ FOOD:TEMP, data=average.all)) 
TukeyHSD(aov(Length ~ FOOD:TEMP, data=average.all)) 

aggregate(Length ~ FOOD:TEMP, data=average.all, mean)
aggregate(Length ~ FOOD:TEMP, data=average.all, sd)
aggregate(Width ~ FOOD:TEMP, data=average.all, mean)
aggregate(Width ~ FOOD:TEMP, data=average.all, sd)

aggregate(Length ~ FOOD:TEMP, data=average.all, min)
aggregate(Length ~ FOOD:TEMP, data=average.all, max)
aggregate(Width ~ FOOD:TEMP, data=average.all, min)
aggregate(Width ~ FOOD:TEMP, data=average.all, max)

mean(average.all$Length)
mean(average.all$Width)

# Plot average larval size ~ average egg size, by treatment 
left_join(
  subset(oocyte.meanlength, TREAT!="Wild") %>%
  mutate_at(c("TEMP", "FOOD"), as.character) %>%
  mutate(TEMP = str_replace_all(TEMP, "COLD", "Cold"),
         TEMP = str_replace_all(TEMP, "WARM", "Warm"),
         FOOD = str_replace_all(FOOD, "HIGH", "High"),
         FOOD = str_replace_all(FOOD, "LOW", "Low")) %>%
  mutate_at(c("TEMP", "FOOD"), as.factor) %>%
  group_by(TEMP,FOOD) %>%
  summarise(mean.length.egg = mean(Length, na.rm=TRUE),
            sd.length.egg = sd(Length, na.rm=TRUE)),
  average.all %>% 
  group_by(TEMP,FOOD) %>%
  summarise(mean.length.larvae = mean(Length, na.rm=TRUE),
            sd.length.larvae = sd(Length, na.rm=TRUE))) %>%
  as.data.frame() %>%
  ggplot(aes(x=mean.length.egg, y=mean.length.larvae, col=FOOD:TEMP)) +
  geom_point(size=4, shape=16) +
  theme_bw(base_size = 13) + 
  labs(title="Mean larval size ~ Mean egg size", y=("Mean shell width (µm)"), x="Mean oocyte length (µm)") + 
  scale_color_manual(values=c('#0571b0','darkslateblue','#ca0020','chocolate2'), name=element_blank(), 
    labels = c("Cold / High Food", "Cold / Low Food", "Warm / High Food", "Warm / Low Food")) + 
  theme(text = element_text(size = 12), legend.position = "none") #+
  geom_errorbar(aes(ymin=mean.length.larvae-sd.length.larvae,
                    ymax=mean.length.larvae+sd.length.larvae), width=.2,
                 position=position_dodge(.9)) +
  geom_errorbar(aes(xmin=mean.length.egg-sd.length.egg,
                    xmax=mean.length.egg+sd.length.egg), width=.2,
                 position=position_dodge(.9))
```

### Shell length, reared larvae 

```{r}
# Relevel food factors such that Low comes before High
average.reared$FOOD <- factor(average.reared$FOOD, levels = rev(levels(average.reared$FOOD)))

pdf(file=here::here("results","larval-shell-length-reared-remeasure.pdf"))
average.reared %>%
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=FOOD:TEMP)) + 
  theme_bw(base_size = 11) + 
  labs(title="Larval shell Length\nby parental treatment", y=("shell length (µm)"), x="treatment") + 
  scale_color_manual(values=c('#92c5de','#f4a582','#0571b0','#ca0020'), name=element_blank(), 
  labels = c("Low-food+7°C","Low-food+10°C","High-food+7°C"," High-food+10°C")) + 
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP))
dev.off()

summary(aov(Length ~ FOOD:TEMP, data=average.reared)) 
TukeyHSD(aov(Length ~ FOOD:TEMP, data=average.reared)) 

# PCSGA presentation 
average.reared %>%
mutate(FOOD = factor(FOOD, levels=c("Low", "High"))) %>% 
ggplot(aes(x=FOOD:TEMP, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=FOOD:TEMP), outlier.shape = NA) + 
  theme_bw(base_size = 11) + 
  labs(title="Larval shell length\nby parental treatment", y=("shell length (µm)"), x="treatment") + 
  scale_color_manual(values=c('darkslateblue','#0571b0','chocolate2','#ca0020'), name=element_blank(),
    labels = c("Cold / Low Food", "Cold / High Food", "Warm / Low Food","Warm / High Food")) +
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none") + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) +
  ylim(c(165,203))
```

# Boneyard 

###  MaxFeret

```{r}
average.all %>%
  group_by(TEMP, FOOD) %>%
  summarise(count = n_distinct(sheet))

average.all %>%
ggplot(aes(x=FOOD:TEMP, y=MaxFeret)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
    ggtitle("MaxFeret by treatment") + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) 

hist(average.all$MaxFeret)
shapiro.test(average.all$MaxFeret)
bartlett.test(average.all$MaxFeret ~ average.all$TEMP)
bartlett.test(average.all$MaxFeret ~ average.all$FOOD)
summary(aov(MaxFeret ~ FOOD:TEMP, data=average.all))

# Low food only 
hist(subset(average.all, FOOD=="Low")$MaxFeret)
shapiro.test(subset(average.all, FOOD=="Low")$MaxFeret)
bartlett.test(subset(average.all, FOOD=="Low")$MaxFeret ~ subset(average.all, FOOD=="Low")$TEMP)
summary(lm(MaxFeret ~ TEMP, data=subset(average.all, FOOD=="Low")))
```

### MinFeret 

```{r}
average.all %>%
ggplot(aes(x=FOOD:TEMP, y=MinFeret)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  ggtitle("MinFeret by treatment") + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) 

hist(average.all$MinFeret)
shapiro.test(average.all$MinFeret)
bartlett.test(average.all$MinFeret ~ average.all$TEMP)
bartlett.test(average.all$MinFeret ~ average.all$FOOD)
summary(aov(MinFeret ~ FOOD:TEMP, data=average.all))
summary(aov(MinFeret ~ FOOD:TEMP, data=average.all))
TukeyHSD(aov(MinFeret ~ FOOD:TEMP, data=average.all))
summary(aov(MinFeret ~ Circularity*FOOD*TEMP, data=average.all))
summary(aov(MinFeret ~ Date*FOOD*TEMP, data=average.all))


summary(aov(MinFeret ~ Date*TEMP, data=subset(average.all, FOOD=="Low")))

```

# More stats on only the larvae I reared 

## MaxFeret 

```{r}
average.reared %>%
ggplot(aes(x=FOOD:TEMP, y=MaxFeret)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP)) 

hist(average.reared$Width)
shapiro.test(average.reared$MaxFeret)
bartlett.test(average.reared$MaxFeret ~ average.reared$TEMP)
bartlett.test(average.reared$MaxFeret ~ average.reared$FOOD)
summary(aov(MaxFeret ~ FOOD*TEMP, data=average.reared)) #Food sign. 
TukeyHSD(aov(MaxFeret ~ FOOD*TEMP, data=average.reared)) #Larger larvae from high food broodstock 
summary(aov(MaxFeret ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(MaxFeret ~ FOOD:TEMP, data=average.reared))

summary(aov(MaxFeret ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))
```

## MinFeret 

```{r}
average.reared %>%
ggplot(aes(x=FOOD:TEMP, y=MinFeret)) + 
  geom_boxplot(aes(col=FOOD:TEMP)) + 
  geom_jitter(width=0.2, aes(col=FOOD:TEMP))

hist(average.reared$MinFeret)
shapiro.test(average.reared$MinFeret)
bartlett.test(average.reared$MinFeret ~ average.reared$TEMP)
bartlett.test(average.reared$MinFeret ~ average.reared$FOOD)
summary(aov(MinFeret ~ FOOD*TEMP, data=average.reared)) #food sign. 
TukeyHSD(aov(MinFeret ~ FOOD*TEMP, data=average.reared)) # Larger larve from high food 
summary(aov(MinFeret ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(MinFeret ~ FOOD:TEMP, data=average.reared))

```