---
title: "larval-size"
author: "Laura H Spencer"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(readxl)
require(here)
require(purrr)
require(plotly)

```

Read in size data, join with sample info 

```{r}
# Data collected using Jackie's scope, but done so in numerical order, which was not random. 
larvalsize.path.old <- here::here("data", "new-larvae-size", "20191111_2018-new-larvae.xlsx")
larvalsize.old <- larvalsize.path.old %>%
  excel_sheets() %>%
  set_names() %>%
  purrr::map_df(~ read_excel(path = larvalsize.path.old, sheet = .x), .id = "sheet") %>%
  dplyr::mutate(Sample.number = as.numeric(sheet)) %>% 
  inner_join(
    readRDS(file=here::here("data/larvae-collection-data.rds")) %>% 
      as_tibble() %>%
      dplyr::select(Rep, Date, Bag, Group, Sample.number, Live.Larvae, TEMP, FOOD, TREAT) %>%
      dplyr::mutate(Sample.number = as.numeric(Sample.number)))

# Data re-collected using Jackie's scope, in random order. 
larvalsize.path <- here::here("data", "new-larvae-size", "20200110_2018-new-larvae.xlsx")
larvalsize <- larvalsize.path %>%
  excel_sheets() %>%
  set_names() %>%
  purrr::map_df(~ read_excel(path = larvalsize.path, sheet = .x), .id = "sheet") %>%
  dplyr::mutate(Sample.number = as.numeric(sheet)) %>% 
  inner_join(
    readRDS(file=here::here("data/larvae-collection-data.rds")) %>% 
      as_tibble() %>%
      dplyr::select(Rep, Date, Bag, Group, Sample.number, Live.Larvae, TEMP, FOOD, TREAT) %>%
      dplyr::mutate(Sample.number = as.numeric(Sample.number)))
```

How many larvae were measured per sample? 

```{r}
ngroups <- larvalsize %>% group_by(sheet) %>% tally()
```


Create a dataframe with average shell measurements by sample number (aka larval batch)

```{r}
average.all <- larvalsize %>% 
  dplyr::select(sheet, MaxFeret, MinFeret, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group, Live.Larvae) %>%
  group_by(sheet) %>%
  mutate_at(c("MaxFeret", "MinFeret", "Circularity", "Length", "Width", "Live.Larvae"), mean, na.rm=TRUE) %>%
  distinct()
```

# Plots

## Length & Width by release date 

```{r}
ggplotly(average.all %>% 
ggplot(aes(x=sheet, y=Length, col=TEMP:FOOD)) + theme(legend.position="bottom", 
       axis.text.x = element_text(angle = 90, hjust = 1, size = 6)) + 
  ggtitle("Length, proxy for shell width") + geom_point())

ggplotly(average.all %>% 
ggplot(aes(x=sheet, y=Width, col=TEMP:FOOD)) + theme(legend.position="bottom", 
       axis.text.x = element_text(angle = 90, hjust = 1, size = 6)) + 
  ggtitle("Width, proxy for shell height") + geom_point())
```

## Shell size by circulatiry (which may influence how accurate measurements were)

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Circularity, y=Length, col=TEMP:FOOD)) + 
  geom_point() + ggtitle("Length, proxy for shell width") +
  geom_smooth(method = "lm", alpha = .15, aes(fill = TEMP:FOOD)))

ggplotly(average.all %>%
ggplot(aes(x=Circularity, y=Width, col=TEMP:FOOD)) + 
  geom_point() + ggtitle("Width, proxy for shell height") +
  geom_smooth(method = "lm", alpha = .15, aes(fill = TEMP:FOOD)))
```

## Shell size by date released 

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Date, y=Length, col=TEMP:FOOD)) + 
  geom_point() + 
  geom_smooth(method = "lm", alpha = .15, aes(fill = TEMP:FOOD)))

ggplotly(average.all %>%
ggplot(aes(x=Date, y=Width, col=TEMP:FOOD)) + 
  geom_point() + 
  geom_smooth(method = "lm", alpha = .15, aes(fill = TEMP:FOOD)))
```

## Circularity by release date

### NOTE: it is clear that samples #1-50 were preserved well, but samples >#50 were considerably degraded (ethanol was not used to kill the larvae)

```{r}
ggplotly(average.all %>%
ggplot(aes(x=sheet, y=Circularity, col=TEMP:FOOD)) + 
  geom_point())
```

## Shell length by # larvae collected that day 

```{r}
ggplotly(average.all %>%
ggplot(aes(x=Live.Larvae, y=Length, col=TEMP:FOOD)) + 
  geom_point())
```


```{r}
### plot old vs. new measurements - different? 

old.new <- merge(
  x=larvalsize.old %>% 
  dplyr::select(sheet, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group) %>%
  group_by(sheet) %>%
  mutate_at(c("Length", "Width", "Circularity"), mean, na.rm=TRUE) %>%
  distinct(),
  y=larvalsize %>% 
  dplyr::select(sheet, Length, Width, Circularity, Sample.number, Date, TEMP, FOOD, Group) %>%
  group_by(sheet) %>%
  mutate_at(c("Length", "Width", "Circularity"), mean, na.rm=TRUE) %>%
  distinct(),
  by="sheet") 

summary(lm(Length.y ~ Length.x, data=old.new))

ggplotly(ggplot(data=old.new, aes(x=Length.x, y=Length.y, col=TEMP.x:FOOD.x)) + 
  geom_point() + geom_smooth(method = "lm"))

ggplotly(ggplot(data=old.new, aes(x=Length.x, y=Length.y)) + 
  geom_point() + geom_smooth(method = "lm"))

```

### Boxplots analysis of size metrics by treatment, all larvae measured 

###  MaxFeret

```{r}
average.all %>%
  group_by(TEMP, FOOD) %>%
  summarise(count = n_distinct(sheet))

average.all %>%
ggplot(aes(x=TEMP:FOOD, y=MaxFeret)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
    ggtitle("MaxFeret by treatment") + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.all$MaxFeret)
shapiro.test(average.all$MaxFeret)
bartlett.test(average.all$MaxFeret ~ average.all$TEMP)
bartlett.test(average.all$MaxFeret ~ average.all$FOOD)
summary(aov(MaxFeret ~ TEMP*FOOD, data=average.all))

# Low food only 
hist(subset(average.all, FOOD=="Low")$MaxFeret)
shapiro.test(subset(average.all, FOOD=="Low")$MaxFeret)
bartlett.test(subset(average.all, FOOD=="Low")$MaxFeret ~ subset(average.all, FOOD=="Low")$TEMP)
summary(lm(MaxFeret ~ TEMP, data=subset(average.all, FOOD=="Low")))
```

### MinFeret 

```{r}
average.all %>%
ggplot(aes(x=TEMP:FOOD, y=MinFeret)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  ggtitle("MinFeret by treatment") + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.all$MinFeret)
shapiro.test(average.all$MinFeret)
bartlett.test(average.all$MinFeret ~ average.all$TEMP)
bartlett.test(average.all$MinFeret ~ average.all$FOOD)
summary(aov(MinFeret ~ TEMP*FOOD, data=average.all))
summary(aov(MinFeret ~ FOOD:TEMP, data=average.all))
TukeyHSD(aov(MinFeret ~ FOOD:TEMP, data=average.all))
summary(aov(MinFeret ~ Circularity*FOOD*TEMP, data=average.all))
summary(aov(MinFeret ~ Date*FOOD*TEMP, data=average.all))


summary(aov(MinFeret ~ Date*TEMP, data=subset(average.all, FOOD=="Low")))

```

### Length

```{r}
average.all %>%
ggplot(aes(x=TEMP:FOOD, y=Length)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  ggtitle("Length by treatment") + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.all$Length)
shapiro.test(average.all$Length)
bartlett.test(average.all$Length ~ average.all$TEMP)
bartlett.test(average.all$Length ~ average.all$FOOD)
summary(aov(Length ~ TEMP*FOOD, data=average.all)) 
plot(lm(Length ~ TEMP*FOOD, data=average.all))

mean(average.all$Length)
mean(average.all$Width)

summary(aov(Length ~ TEMP, data=subset(average.all, FOOD=="Low"))) 
```

### Width

```{r}
average.all %>%
ggplot(aes(x=TEMP:FOOD, y=Width)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  ggtitle("Width by treatment") + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.all$Width)
shapiro.test(average.all$Width)
bartlett.test(average.all$Width ~ average.all$TEMP)
bartlett.test(average.all$Width ~ average.all$FOOD)
summary(aov(Width ~ TEMP*FOOD, data=average.all))
summary(aov(Width ~ Circularity*FOOD*TEMP, data=average.all))
plot(lm(Width ~ TEMP*FOOD, data=average.all))

summary(aov(Width ~ TEMP, data=subset(average.all, FOOD=="Low"))) 
```

# Assess larval size differences among only larval groups that I reared, by broodstock treatment

```{r}
average.reared <- larvalsize %>% 
  dplyr::select(sheet, MaxFeret, MinFeret, Circularity, Length, Width, Sample.number, Date, TEMP, FOOD, Group) %>%
  filter(!is.na(Group)) %>%
  group_by(sheet) %>%
  mutate_at(c("MaxFeret", "MinFeret", "Circularity", "Length", "Width"), mean, na.rm=TRUE) %>%
  distinct()
```

## MaxFeret 
```{r}
average.reared %>%
ggplot(aes(x=TEMP:FOOD, y=MaxFeret)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.reared$Width)
shapiro.test(average.reared$MaxFeret)
bartlett.test(average.reared$MaxFeret ~ average.reared$TEMP)
bartlett.test(average.reared$MaxFeret ~ average.reared$FOOD)
summary(aov(MaxFeret ~ TEMP*FOOD, data=average.reared)) #Food sign. 
TukeyHSD(aov(MaxFeret ~ TEMP*FOOD, data=average.reared)) #Larger larvae from high food broodstock 
summary(aov(MaxFeret ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(MaxFeret ~ TEMP*FOOD, data=average.reared))

summary(aov(MaxFeret ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))
```

## MinFeret 

```{r}
average.reared %>%
ggplot(aes(x=TEMP:FOOD, y=MinFeret)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD))

hist(average.reared$MinFeret)
shapiro.test(average.reared$MinFeret)
bartlett.test(average.reared$MinFeret ~ average.reared$TEMP)
bartlett.test(average.reared$MinFeret ~ average.reared$FOOD)
summary(aov(MinFeret ~ TEMP*FOOD, data=average.reared)) #food sign. 
TukeyHSD(aov(MinFeret ~ TEMP*FOOD, data=average.reared)) # Larger larve from high food 
summary(aov(MinFeret ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(MinFeret ~ TEMP*FOOD, data=average.reared))

summary(aov(MinFeret ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))

```

## Length (aka shell width)

```{r}
average.reared %>%
ggplot(aes(x=TEMP:FOOD, y=Length)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.reared$Length)
shapiro.test(average.reared$Length)
bartlett.test(average.reared$Length ~ average.reared$TEMP)
bartlett.test(average.reared$Length ~ average.reared$FOOD)
summary(aov(Length ~ TEMP*FOOD, data=average.reared)) #Food sign. 
TukeyHSD(aov(Length ~ TEMP*FOOD, data=average.reared)) #Larger larvae from high food 
summary(aov(Length ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(Length ~ TEMP*FOOD, data=average.reared))

summary(aov(Length ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))
```

## Width (aka shell height)

```{r}
average.reared %>%
ggplot(aes(x=TEMP:FOOD, y=Width)) + 
  geom_boxplot(aes(col=TEMP:FOOD)) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) 

hist(average.reared$Width)
shapiro.test(average.reared$Width)
bartlett.test(average.reared$Width ~ average.reared$TEMP)
bartlett.test(average.reared$Width ~ average.reared$FOOD)
summary(aov(Width ~ TEMP*FOOD, data=average.reared)) #Food sign. 
TukeyHSD(aov(Width ~ TEMP*FOOD, data=average.reared)) #Lager larvae from high food 
summary(aov(Width ~ Circularity*FOOD*TEMP, data=average.reared))
#plot(lm(Width ~ TEMP*FOOD, data=average.reared))

summary(aov(Width ~ Circularity*TEMP, data=subset(average.reared, FOOD=="Low")))

average.reared %>%
ggplot(aes(x=Circularity, y=Width)) + 
  geom_point(aes(col=TEMP)) 
```

## Figures 

### Shell width (longest axis, but referred to as "length" in data), all measured larvae 

```{r}
pdf(file=here::here("results","larval-shell-length-remeasure.pdf"), width = 6, height = 6)
average.all %>%
ggplot(aes(x=TEMP:FOOD, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=TEMP:FOOD)) + 
  theme_bw(base_size = 13) + 
  labs(title="Larval shell width upon release", y=("shell width (µm)"), x="treatment") + 
  scale_color_manual(values=c('#0571b0','#92c5de','#ca0020','#f4a582'), name=element_blank(), 
    labels = c("Cold / High Food", "Cold / Low Food", "Warm / High Food", "Warm / Low Food")) + 
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  ylim(c(160, 215)) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD))
dev.off()

summary(aov(Length ~ TEMP*FOOD, data=average.all)) 
TukeyHSD(aov(Length ~ TEMP*FOOD, data=average.all)) 

aggregate(Length ~ TEMP*FOOD, data=average.all, mean)
aggregate(Length ~ TEMP*FOOD, data=average.all, sd)
aggregate(Width ~ TEMP*FOOD, data=average.all, mean)
aggregate(Width ~ TEMP*FOOD, data=average.all, sd)

aggregate(Length ~ TEMP*FOOD, data=average.all, min)
aggregate(Length ~ TEMP*FOOD, data=average.all, max)
aggregate(Width ~ TEMP*FOOD, data=average.all, min)
aggregate(Width ~ TEMP*FOOD, data=average.all, max)

mean(average.all$Length)
mean(average.all$Width)

# Plot average larval size ~ average egg size, by treatment 
left_join(
  subset(oocyte.meanlength, TREAT!="Wild") %>%
  mutate_at(c("TEMP", "FOOD"), as.character) %>%
  mutate(TEMP = str_replace_all(TEMP, "COLD", "Cold"),
         TEMP = str_replace_all(TEMP, "WARM", "Warm"),
         FOOD = str_replace_all(FOOD, "HIGH", "High"),
         FOOD = str_replace_all(FOOD, "LOW", "Low")) %>%
  mutate_at(c("TEMP", "FOOD"), as.factor) %>%
  group_by(TEMP,FOOD) %>%
  summarise(mean.length.egg = mean(Length, na.rm=TRUE),
            sd.length.egg = sd(Length, na.rm=TRUE)),
  average.all %>% 
  group_by(TEMP,FOOD) %>%
  summarise(mean.length.larvae = mean(Length, na.rm=TRUE),
            sd.length.larvae = sd(Length, na.rm=TRUE))) %>%
  as.data.frame() %>%
  ggplot(aes(x=mean.length.egg, y=mean.length.larvae, col=TEMP:FOOD)) +
  geom_point(size=4, shape=16) +
  theme_bw(base_size = 13) + 
  labs(title="Mean larval size ~ Mean egg size", y=("Mean shell width (µm)"), x="Mean oocyte length (µm)") + 
  scale_color_manual(values=c('#0571b0','darkslateblue','#ca0020','chocolate2'), name=element_blank(), 
    labels = c("Cold / High Food", "Cold / Low Food", "Warm / High Food", "Warm / Low Food")) + 
  theme(text = element_text(size = 12), legend.position = "none") #+
  geom_errorbar(aes(ymin=mean.length.larvae-sd.length.larvae,
                    ymax=mean.length.larvae+sd.length.larvae), width=.2,
                 position=position_dodge(.9)) +
  geom_errorbar(aes(xmin=mean.length.egg-sd.length.egg,
                    xmax=mean.length.egg+sd.length.egg), width=.2,
                 position=position_dodge(.9))
```

### Shell length, reared larvae 

```{r}
pdf(file=here::here("results","larval-shell-length-reared-remeasure.pdf"))
average.reared %>%
ggplot(aes(x=TEMP:FOOD, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=TEMP:FOOD)) + 
  theme_bw(base_size = 11) + 
  labs(title="Larval shell Length\nby parental treatment", y=("shell length (µm)"), x="treatment") + scale_color_manual(
    values=c('#0571b0','#92c5de','#ca0020','#f4a582'), name=element_blank(), 
    labels = c("Cold / High Food", "Cold / Low Food", "Warm / High Food", "Warm / Low Food")) + 
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD))
dev.off()

summary(aov(Length ~ TEMP*FOOD, data=average.reared)) 
TukeyHSD(aov(Length ~ TEMP*FOOD, data=average.reared)) 

# PCSGA presentation 
average.reared %>%
mutate(FOOD = factor(FOOD, levels=c("Low", "High"))) %>% 
ggplot(aes(x=TEMP:FOOD, y=Length)) + 
geom_boxplot(lwd=0.5, aes(col=TEMP:FOOD), outlier.shape = NA) + 
  theme_bw(base_size = 11) + 
  labs(title="Larval shell length\nby parental treatment", y=("shell length (µm)"), x="treatment") + 
  scale_color_manual(values=c('darkslateblue','#0571b0','chocolate2','#ca0020'), name=element_blank(),
    labels = c("Cold / Low Food", "Cold / High Food", "Warm / Low Food","Warm / High Food")) +
  theme(text = element_text(size = 12)) + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none") + 
  geom_jitter(width=0.2, aes(col=TEMP:FOOD)) +
  ylim(c(165,203))
```

